\documentclass{article}

\usepackage{comment}
\usepackage{amsmath, amssymb}

\newcommand{\bigO}{\mathcal{O}}
\newtheorem{definition}{Definition}

\title{Generating, Ranking, and Unranking Integer Compositions with Distinct Parts}
\author{Joseph Wood}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}

Combinatorial objects possess the extraordinary quality of simultaneously being easy to explain and devilishly difficult to maneuver. Take for example the integer composition with distinct parts:

They also have a remarkably similar pattern of adoption. At first, a definition followed by an example or two. After that, we want to know if we can count them. Is there a closed form? Then come the questions around generation. Ultimately, we arrive at a place where we want to answer something much stronger: Given any valid object, can we generate the next one faithfully? This last bit is known as lexicographic generation and if we get this far, it is natural to start thinking about ranking and unranking.

All of these questions have exhaustive answers with many combinatorial objects such as combinations, permutations, and even some forms of integer compositions. However, when it comes to integer compositions with distinct parts, generating them has been largely elusive. We present here an efficient algorithm for generating integer compositions with distinct parts as well as algorithms for ranking and unranking them.
    
\end{abstract}

\input{sections/introduction}
\input{sections/preliminaries}

\begin{comment}
\input{sections/related_work}
\input{sections/standard_algorithm}
\input{sections/distinct_case}
\input{sections/extensions}
\input{sections/complexity}
\input{sections/implementation}
\input{sections/results}
\input{sections/conclusion}
\end{comment}

\end{document}
